NHF1 General Read Sequence Figure Generation

### 2022-05-24 R/NHF1GeneralReadSequenceDataGeneration.rmd
Update R notebooks

```{r define_all_that_and_a_bag_of_chips_function}
singleFileFullAnalysis = function(lesion, repitition, timepoint) {
  readData = fread(generateFilePath(
    generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repitition, expansionNum = expansionOffset
  ))
  readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
  readData = readData[Read_Length >= 20 & Read_Length <= 31]

>>>>

```{r define_all_that_and_a_bag_of_chips_function}
singleFileFullAnalysis = function(lesion, repitition, timepoint) {
  readData = fread(generateFilePath(
    generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
    cellType = cellType, lesion = lesion, timepoint = timepoint,
    repitition = repitition, expansionNum = expansionOffset
  ))
  readData = data.table(Read_Length = nchar(readData$V7)-expansionOffset*2, Read_Sequence = readData$V7)
  readData = readData[Read_Length >= 15 & Read_Length <= 31]

### 2022-05-24 R/NHF1GeneralReadSequenceFigureGeneration.rmd
Update R notebooks

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 7}
plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

@@

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 7}
plotSequenceFrequencies(sixFourTGGSeqFreq$rep1,
                        title = "6-4 TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(sixFourTGGSeqFreq$rep2,
                        title = "6-4 TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

@@

  readData = timepoints
  for (i in seq_along(readData)) {
    readData[[i]] = fread(generateFilePath(
      generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
      cellType = cellType, lesion = lesion, timepoint = names(readData)[i],
      repitition = repitition, expansionNum = expansionOffset
    ))
    readData[[i]] = data.table(Read_Length = nchar(readData[[i]]$V7)-expansionOffset*2,
                               Timepoint = names(readData)[i])
    readData[[i]] = readData[[i]][Read_Length >= 20 & Read_Length <= 31]
  }

@@

```{r 6-4_read_length_frequencies}
plotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
plotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
```

>>>>

```{r CPD_sequence_frequencies, fig.width = 11, fig.height = 10}
plotSequenceFrequencies(CPDTGGSeqFreq$rep1,
                        title = "CPD TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(CPDTGGSeqFreq$rep2,
                        title = "CPD TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

@@

```{r 6-4_sequence_frequencies, fig.width = 11, fig.height = 10}
plotSequenceFrequencies(sixFourTGGSeqFreq$rep1,
                        title = "6-4 TGG Frequencies Rep1", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))
plotSequenceFrequencies(sixFourTGGSeqFreq$rep2,
                        title = "6-4 TGG Frequencies Rep2", expansionOffset = expansionOffset,
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE,
                        querySequences = c("TGG"))

@@

  readData = timepoints
  for (i in seq_along(readData)) {
    readData[[i]] = fread(generateFilePath(
      generalReadSequenceDataDirectory, dataTypeStrings$alignedReads, ".bed",
      cellType = cellType, lesion = lesion, timepoint = names(readData)[i],
      repitition = repitition, expansionNum = expansionOffset
    ))
    readData[[i]] = data.table(Read_Length = nchar(readData[[i]]$V7)-expansionOffset*2,
                               Timepoint = names(readData)[i])
    readData[[i]] = readData[[i]][Read_Length >= 15 & Read_Length <= 31]
  }

@@

```{r 6-4_read_length_frequencies}
readAndPlotReadLengthFrequencies("6-4", "rep1", sixFourTimepoints)
readAndPlotReadLengthFrequencies("6-4", "rep2", sixFourTimepoints)
```
